---
title: "Organizers and Contact Information"
output:
  html_document:
    toc: false
---

<<<<<<< HEAD
<!-- The file analysis/chunks.R contains chunks that define default settings
shared across the workflowr files. -->
```{r read-chunk, include=FALSE, cache=FALSE}
knitr::read_chunk("chunks.R")
```

<!-- Update knitr chunk options -->
```{r knitr-opts-chunk, include=FALSE}
```

<!-- Insert the date the file was last updated -->
```{r last-updated, echo=FALSE, results='asis'}
```

<!-- Insert the code version (Git commit SHA1) if Git repository exists and R
 package git2r is installed -->
```{r code-version, echo=FALSE, results='asis'}
```
Coming soon

## Session information

<!-- Insert the session information into the document -->
```{r session-info}
```
=======

### Nicholas George
Graduate Student
NICHOLAS.M.GEORGE@UCDENVER.EDU
Anschutz Campus - Sch of Med - Cell and Developmental Bio

### Joshua Johnson
Assistant Professor
Division of Reproductive Sciences
Department of Obstetrics and Gynecology
University of Colorado Denver (AMC)
Building RC2, Room P15 3103
Mail Stop 8613
Aurora, Colorado 80045

Office: 303.724.7281
Mobile: 203.889.8123
Email: joshua.2.johnson@ucdenver.edu

### Wladimir Labeikovski
Health Sciences Library
UC Denver | Anschutz Medical Campus
orcid.org/0000-0001-6074-3269

### Tzu Phang
Tzu.Phang@ucdenver.edu
Research II : room 9400 D
Anschutz Campus - Sch of Med - BIOMED
>>>>>>> d5bceb64f6b0c771d7ef4ecad2bbf92c1ad99fb8
